The Astropy Project

### 2017-11-13 main.tex
ascii (add pandas citation) and fits scripts

    \item[\texttt{.ascii}: fast reader/writer]

        The \package{astropy.io.ascii} module now includes a significantly faster
        Cython/C engine for reading and writing ASCII files. This is available
        for the following formats: basic, commented\_header, csv, no\_header,
        rdb, and tab.  On average the new engine is about 4 to 5 times faster
        than the corresponding pure-\python implementation, and is often
        comparable to the speed of the pandas ASCII file interface. The fast
        reader has parallel processing option that allows harnessing multiple
        cores for input parsing to achieve even greater speed gains.

@@

        The \package{astropy.io.fits} subpackage now provides a command line
        script for inspecting the header(s) of a FITS file.  Running
        \texttt{fitsheader file.fits} in a terminal prints the header
        information to the screen in a human-readable format. Run
        \texttt{fitsheader --help} to see the full usage documentation.

@@

        The \package{astropy.io.fits} subpackage now supports \emph{lazy
        loading}, where all HDUs are not loaded until they are requested (or
        the file is closed). This should provide substantial speedups for
        situations using the convenience functions (e.g., \texttt{getheader()}
        or \texttt{getdata()}) to get HDU’s that are near the front of a file
        with many HDU’s.

>>>>

    \item[\texttt{.ascii}: fast readers and writers]

        The \package{astropy.io.ascii} module now includes a significantly
        faster Cython/C engine for reading and writing ASCII files. This is
        available for the following formats: \texttt{basic},
        \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
        \texttt{rdb}, and \texttt{tab}.  On average the new engine is about
        4 to 5 times faster than the corresponding pure-\python
        implementation, and is often comparable to the speed of the
        \package{Pandas} \citep{pandas} ASCII file interface.  The fast
        reader has parallel processing option that allows harnessing
        multiple cores for input parsing to achieve even greater speed
        gains.

@@

        The \package{astropy.io.fits} subpackage now provides command-line
        scripts for printing a summary of the HDUs in a FITS file(s)
        (\texttt{fitsinfo file.fits}) and for printing the header information
        to the screen in a human-readable format (\texttt{fitsheader
        file.fits}).

@@

        The \package{astropy.io.fits} subpackage now supports \emph{lazy
        loading}, where all HDUs are not loaded until they are requested (or
        the file is closed). This should provide substantial speedups for
        situations using the convenience functions (e.g., \texttt{getheader()}
        or \texttt{getdata()}) to get HDU’s that are near the front of a file
        with many HDUs.
